Multi-Index and Multi-Level Monte Carlo Evaluation of HJM Models

### 2016-05-08 tests/HJM/manuscript.tex
fig 3 rereplot

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr2.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr2.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig2} Weak (left) and strong (right) error
    for frequency cutoff
    $\nnorm{\Psi_{2N_f}-\Psi_{N_f}}{}$ together with the $N_f^{-\frac{3}{2}}$ and
    $N_f^{-3}$ reference lines in red.}
\end{figure}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr2.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr2.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig2} Bias (left) and variance (right) error
    for frequency cutoff
    $\nnorm{\Psi_{2N_f}-\Psi_{N_f}}{}$ together with the $N_f^{-\frac{3}{2}}$ and
    $N_f^{-3}$ reference lines in red.}
\end{figure}
